Title: A proof-of-concept study

### 2022-01-08 paper.tex
update

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through the jet sources show that the dense disk not only helps the bubbles to align the disk normal\
             but also creates an under pressure, cold, and dense bubble in the most inner region.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

>>>>

\author{Chun-Yen Chen}
\affiliation{Institute of physics, National Taiwan University, Taipei 10617, Taiwan}

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different circumstances.\
             Comparison between the cases with a clumpy (first column from left)\
             and a smooth disk (second) in a stratified atmosphere\
             shows that the density distribution of the dense disk has insignificant effect\
             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (third)\
             in an uniform atmosphere is spherical-shape,\
             suggesting the stratification facilitates bubbles elongation significantly.\

             The first three and the rightmost columns shows that the under pressure, cold, and dense bubbles
             the bubbles without disk is tilted even\
             in the stratified atmosphere, and

             and the under pressure, cold, and dense bubbles (dashed box)\
             is also evident in the first three columns,

             indicating dense disk is a crucial component for axis-symmetric bubbles formation.\

             Comparing all cases show that the under pressure, cold, and dense bubbles (dashed box)\
             ionly appear if disk is present.

             The first three diagrams and the rightmost diagram show that the air bubbles can only be generated\
             with the disk and without the disk, the air bubbles will be skewed.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}
